### 2021-01-09 paper/appendix.tex
Small edits.
Draft of full semantics.

@@

@@

@@

>>>>

\subsection{Reads Update Local State}
In the rule for read prefixing we have substituted $[r/x]$, rather than
$[x/r]$.  This means that reads clobber local state.  We assume registers are
only used once---otherwise, one needs to generate a fresh register for the
substitution.

With read-read dependencies, this difference can be seen.  For example, the
following execution is allowed with $[x/r]$, but not $[r/x]$.
\begin{gather*}
  \PW{x}{0}\SEMI
  \PR{x}{r}\SEMI
  \IF{r}\THEN \PR{x}{s}\FI\SEMI
  \PW{y}{s{+}1}
  \PAR
  \PW{x}{\PR{y}{}}
  \\[-1ex]
  \hbox{\begin{tikzinline}[node distance=1.5em]
      \event{a1}{\DW{x}{0}}{}
      \event{a2}{\DW{x}{1}}{right=of a1}
      \event{a3}{\DR{x}{0}}{right=of a2}
      \event{a4}{\DW{y}{1}}{right=of a3}
      \event{b1}{\DR{y}{1}}{right=3em of a4}
      \event{b2}{\DW{x}{1}}{right=of b1}
      \wk{a1}{a2}
      \po{a2}{a3}
      \po{b1}{b2}
      \rf{a4}{b1}
      \rf[out=165,in=15]{b2}{a2}
    \end{tikzinline}}
\end{gather*}
[Is there a difference w/o read-read dependencies?]

\subsection{Parallel Composition}

@@

\subsection{Redundant Read Elimination}

@@

\subsection{Internal Acquiring Reads}

@@

The notion of data-race is incorrect in \jjr{}.
\begin{gather*}
  \PW{x}{1}\SEMI
  \PW[\mRA]{y}{1}\SEMI
  \PR[\mRA]{x}{r}
  \PAR
  \IF{\PR[\mRA]{y}{}}\THEN \PW[\mRA]{x}{2}\FI
  \\
  \hbox{\begin{tikzinline}[node distance=1.5em]
      \event{a1}{\DW{x}{1}}{}
      \event{a2}{\DW[\mRA]{y}{1}}{right=of a1}
      \event{a3}{\DR[\mRA]{x}{1}}{right=of a2}
      \event{b1}{\DR[\mRA]{y}{1}}{right=3em of a3}
      \event{b2}{\DW[\mRA]{x}{2}}{right=of b1}
      \sync{a1}{a2}
      \rf[out=20,in=160]{a1}{a3}
      \rf[out=20,in=160]{a2}{b1}
      \sync{b1}{b2}
    \end{tikzinline}}
  \\
  \hbox{\begin{tikzinline}[node distance=1.5em]
      \event{a1}{\DW{x}{1}}{}
      \event{a2}{\DW[\mRA]{y}{1}}{right=of a1}
      \event{a3}{\DR[\mRA]{x}{2}}{right=of a2}
      \event{b1}{\DR[\mRA]{y}{1}}{right=3em of a3}
      \event{b2}{\DW[\mRA]{x}{2}}{right=of b1}
      \sync{a1}{a2}
      \rf[out=20,in=160]{a2}{b1}
      \rf[out=160,in=20]{b2}{a3}
      \sync{b1}{b2}
    \end{tikzinline}}
\end{gather*}
Bug is in \citep[Lemma A.4]{DBLP:conf/ppopp/DongolJR19}.  It assumes that
$\DRP[\mRA]{x}{1}$ and $\DWP[\mRA]{x}{2}$ are racing in the first execution
because they are not ordered by happens-before.  But this is false since
neither is plain.
